HiC Contact Map Comaprison Using Graphlet Approach

### 2018-03-27 papers/manuscripts/manuscript.tex
modified manuscript

We caclulated pair-wise MIC for each orbit in each of the 276
contact maps from MIT data and ALL, RL and CALL4 data separately. 
Figure \ref{fig:contact_maps_correlations}
shows average orbit correlations across all contact maps
($\bar{\mathbf{c}}^{\scriptscriptstyle A,B}_{i,j}$: average along the red \textit{vertical} arrow in figure 
\ref{graphlet_correlation_schema}), while
figure \ref{fig:orbits_correlations} 
demonstrates average correlations across all 72 orbits within each  contact map
(average along the red \textit{horizontal} arrows in figure 
\ref{graphlet_correlation_schema}).
It is worth mentioning that \textit{interchromosomal} thresholded contact maps 
represent
a biparticde graph with the loci from each chromosome on one side. Due to this
bipartide nature of the graphs in inter-chromosomal maps,
count of certain orbits is always 0, resulting in
a correlation values of 0 for them as well.
We ignored these values  when we calculated averages across orbits 
in figure \ref{fig:contact_maps_correlations_all} since they
would result in a bias towards zero in averages. You can see the bias in 
figure \ref{fig:orbits_correlations_all} where average correlations of obits
3, 9, 10-14, 20-34, 39-48, and 51-72 are close to zero. In fact all correlations
corresponding to these orbits are 0 except for the ones between the same 
chromosomes which are illustrated in Figure 
\ref{fig:orbits_correlations_intra}.

>>>>

We caclulated pair-wise MIC for each orbit in each of the 276
contact maps from MIT data and ALL, RL and CALL4 data separately. 
Figure \ref{fig:contact_maps_correlations}
shows average orbit correlations across all contact maps
($\bar{\mathbf{c}}^{\scriptscriptstyle A,B}_{i,j} 
\quad \forall i,j \in {1 ... 23} \quad \& \quad j \le i$,
average along the red \textit{vertical} arrow in figure 
\ref{graphlet_correlation_schema}), while
figure \ref{fig:orbits_correlations} 
demonstrates average correlations across all 72 orbits within each  contact map
($\frac{1}{276}\sum_{i=0}^{23}\sum_{j=i}^{23}{
    c^{\scriptscriptstyle A,B}_{i,j}}$,
average along the red \textit{horizontal} arrows in figure 
\ref{graphlet_correlation_schema}).
It is worth mentioning that \textit{interchromosomal} thresholded contact maps 
represent
a biparticde graph with the loci from each chromosome on one side. Due to this
bipartide nature of the graphs in inter-chromosomal maps,
count of certain orbits is always 0, resulting in
a correlation values of 0 for them as well.
We ignored these values  when we calculated averages across orbits 
in figure \ref{fig:contact_maps_correlations_all} since they
would result in a bias towards zero in averages. You can see the bias in 
figure \ref{fig:orbits_correlations_all} where average correlations of obits
3, 9, 10-14, 20-34, 39-48, and 51-72 are close to zero. In fact all correlations
corresponding to these orbits are 0 except for the ones between the same 
chromosomes which are illustrated in Figure 
\ref{fig:orbits_correlations_intra}.
